Based on polling as of 27 October 2024, Harris expects to win on xxx%, leads Trump by xx% in 2024 US election

### 2024-10-30 paper/paper.qmd
Add the result part

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

#### Load Required Libraries ####
library(dplyr)
library(ggplot2)
library(lubridate)
harris_data <- harris_data %>%
  mutate(
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
    predicted_support = predict(model_harris_weighted, newdata = .),
    candidate = "Harris"
  )

trump_data <- trump_data %>%
  mutate(
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight,
    predicted_support = predict(model_trump_weighted, newdata = .),
    candidate = "Trump"
  )

# Combine both datasets
combined_data <- bind_rows(harris_data, trump_data)

#### Plot Support Trends by State with Reduced Date Labels ####
# Define states of interest
selected_states <- c("Pennsylvania", "Nevada", "North Carolina", "Wisconsin", "Michigan", "Georgia", "Arizona")

# Filter data for selected states
combined_data <- combined_data %>% filter(state %in% selected_states)

# Create the faceted plot with limited x-axis labels
ggplot(combined_data, aes(x = as.Date(end_date), y = predicted_support, color = candidate, size = combined_weight)) +
  geom_point(alpha = 0.6) +
  scale_color_manual(values = c("Harris" = "#1f77b4", "Trump" = "#d62728")) +  # Blue for Harris, Red for Trump
  scale_size_continuous(range = c(1, 4)) +  # Control point size range for readability
  scale_x_date(date_labels = "%b %d", date_breaks = "1 month") +  # Show only the first day of each month
  labs(title = "Support Trends for Harris and Trump Across States",
       x = "Date", y = "Support (%)", color = "Candidate") +
  facet_wrap(~ state, ncol = 2, scales = "free_y") +  # Facet by state with free y-scale
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    strip.text = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Slight tilt for x-axis labels
    panel.grid.major = element_line(size = 0.2, linetype = "dotted", color = "gray80"),
    panel.grid.minor = element_blank()
  )
```

>>>>

## Recent 3 Months Support Trends Prediction

The recent three-month support trends for Kamala Harris and Donald Trump across key battleground states—Arizona, Georgia, Michigan, Nevada, North Carolina, Pennsylvania, and Wisconsin—show a highly competitive race. Each state’s panel displays support percentages over time from August to November 2024, with Harris shown in blue and Trump in red. The plot uses point size to represent poll weights, accounting for factors such as recency, pollster quality, and sample size, where larger points indicate higher-weighted polls, emphasizing more reliable data.

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| label: fig-support-trends
#| fig-cap: Support Trends for Kamala Harris and Donald Trump Across Selected States

# Load necessary libraries
library(tidyverse)
library(ggplot2)

harris_data <- harris_data %>%
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    pollster_quality_weight = numeric_grade / 4,
    recency_weight = exp(-recency * 0.1)
  ) %>%
  group_by(pollster) %>%
  mutate(
    recent_poll_count = sum(recency < 30),
    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
  ) %>%
  ungroup() %>%
  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)

# Calculate weights for Trump data
trump_data <- trump_data %>%
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    pollster_quality_weight = numeric_grade / 4,
    recency_weight = exp(-recency * 0.1)
  ) %>%
  group_by(pollster) %>%
  mutate(
    recent_poll_count = sum(recency < 30),
    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
  ) %>%
  ungroup() %>%
  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)

selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
recent_date_cutoff <- as.Date("2024-08-01")  # Set cutoff for recent data

harris_filtered <- harris_data %>%
  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)

trump_filtered <- trump_data %>%
  filter(state %in% selected_states, as.Date(end_date) >= recent_date_cutoff)

# Combine datasets for plotting with a new column for candidate
harris_filtered <- harris_filtered %>% mutate(candidate = "Harris")
trump_filtered <- trump_filtered %>% mutate(candidate = "Trump")
combined_data <- bind_rows(harris_filtered, trump_filtered)

# Plot with recent data, specific axis formatting, and smoother trend lines
ggplot(combined_data, aes(x = as.Date(end_date), y = pct, color = candidate, size = combined_weight)) +
  geom_point(alpha = 0.7) + # Adds points with transparency for overlapping data
  geom_smooth(aes(group = candidate), method = "loess", span = 0.2, se = FALSE, size = 1) + # Smoothed trend line
  facet_wrap(~ state) +
  labs(title = "Recent Support Trends for Kamala Harris and Donald Trump Across Selected States",
       x = "Date", y = "Support (%)") +
  scale_x_date(date_labels = "%b", date_breaks = "1 month", limits = as.Date(c("2024-08-01", "2024-10-31"))) +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  scale_size_continuous(range = c(0.5, 3), guide = "none") +
  theme_minimal() +
  theme(
    legend.position = "top",
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    panel.grid.major = element_line(size = 0.1, color = "grey80")
  ) +
  guides(color = guide_legend(title = "Candidate"))
```
@fig-support-trends illustrates the recent support trends for Kamala Harris and Donald Trump across selected battleground states from August to November 2024. Each subplot represents a different state, with support percentages for each candidate displayed over time. Key features include Harris shown in blue and Trump in red, with smoothed trend lines to capture changes over time. The plot's y-axis spans from approximately 30% to 50% support, while the x-axis highlights monthly intervals from August to November. For example, in Arizona, Trump maintains a slight lead with support fluctuating around 50% in October, compared to Harris around 48%. In Georgia, Trump's support reaches just above 49% in late September, whereas Harris hovers closer to 47%. In Wisconsin, both candidates show tightly aligned trends near 48%, highlighting a close race. Each point's size reflects the poll weight—calculated using recency, pollster quality, and sample size—indicating the relative importance of each poll. This visualization emphasizes recent trends in candidate support across key battleground states.
